Update after major correction to *Management induced changes of soil organic carbon on global croplands*

### 2021-06-07 Revisions/Point by point replies - Jonathan Sanderman.md

# Point by point replies - Jonathan Sanderman

0. This MS presents the findings of a spatially explicit implementation of a new IPCC TierII approach to soil carbon stock changes. The authors use this model to calculate how much SOC has been lost due to agriculture but then go on to run the model annually for the period 1975 – 2010 to produce a dynamic picture of SOC recovery over this modern era of farming.   The major takeaway message is that while agriculture has incurred a large SOC debt, recent agronomic improvements have led to 4 Pg C of SOC sequestration over this period of time. This detailed picture of SOC in croplands over the past several decades is of incredible importance to policy makers and as such I believe that paper can be an important contribution to the literature; however, I do have several major concerns that may or may not be addressable with revisions.

Answer to 0.:
Dear Dr. Sanderman, thank you for the thorough and helpful review of our manuscript. While checking and revising our data processing in response to your and the other reviewer's feedback, we discovered a bug in the very core of the soil model, leading to an overestimation of the transfer of carbon from active to the slow pool *just* for cropland. Additionally, we found unreasonable high forage crop production values (specifically for pumpkins used as fodder) in our input data, which are taken from FAO statistics. This made the overall intensification trend in agriculture lead to increasing carbon stocks in cropland. After correcting the bugs, this is no longer the case. Whereas this implies major revisions of our discussion and interpretation of results, we find that the essence of the paper, which is a) the availability of a soil carbon model that can account for changes in agricultural management and can be applied within integrated assessment frameworks and b) an analysis of the importance of accounting for management dynamics in SOC assessments, remains unchanged, albeit modified. We provide an assessment of how results changed after correcting the bugs as a supplement to this authors comment. Here, we respond point-by-point to the reviewers' comments. Where appropriate, this will also address the implications of the bugfix. We look forward to your response.

1. I had to read the methods section twice and spend an hour with Calvo Buendia et al., 2019 to fully understand what the authors have done. I’m still not 100% confident that I fully understand the methodology. I suggest adding an illustrative example or two graphically demonstrating how the process works. Perhaps starting with a simple case of one lu transition and then showing a more complex case of multiple lu transitions within a pixel.

Answer to 1.:
We will add more detail and graphical representation for demonstrating especially the land-transition accounting.

2. I have not been convinced that this sort of “dynamic” implementation of a steady state modeling approach is appropriate. I understand that the method was developed by the IPCC as a way to add more nuance into the Tier I emission factor approach but I don’t think the method was intended to be applied annually.  Why not go all the way to TierIII approach using the process-based dynamics that are embedded in this simplified model?   It  appears  you  have  all  the  data  assembled  to  do  this.   My  main  concern with applying a steady-state model to annual changes is we know that the recent past trajectory of SOC (particularly in the slow and passive pools) will greatly influence the short-term model response to improved management – i.e.  the model will take years to decades before SOC stocks start to rebuild if the trajectory was negative prior to the change – but this will be completely missed with the steady state application (stocks will start increasing immediately upon change).

Answer to 2.:
This has already been answered in the earlier reply ('Reply on RC1', Kristine Karstens, 26 Jan 2021).

3. What time frame are the monthly climate data averaged over to get the rate modifiers for a steady state solution? Given the passive pool has an intrinsic decay rate equivalent to >100 year turnover time, it seems that you need to have a 100+ year average climate to come up with the proper rate modifiers.

Answer to 3.:
As we do not use a steady state model, we believe the comment might be based on a misunderstanding and no averaging of climate data is needed.

4. Transfer between lu types is not clear.  I do not understand how a “respective share of the SOC is reallocated.”  My concern is that the per area SOC stock for long-term cultivated land will be much different than the per area SOC stock for newly converted cropland, so I don’t see how you can suddenly bin these separate areas into one model component.  Perhaps my request for a visual guide will help me (and other readers)understand that I have misunderstood this part of the methods.

Answer to 4.:
See above: We will add more detail and graphical representation here. This will illustrate the linearity of the problem: Accounting separately for freshly converted cropland and old cropland is in our equation system essentially the same than taking the area weighted mean.

5. Why was 1901 chosen to spin up to steady state?  We know that this was a time of rapid agricultural expansion in several major regions of the world and thus a time of rapid soil carbon loss.

Answer to 5.:
We extended the spin-up phase for a much longer period, starting in 1510 (default spin-up start in LPJmL) to capture the land-use effects. Our initial choice of starting in 1901 was driven by the climate data availability.  To extend our spin-up into the past, we will recycle climate data from 1901 to 1930, as this is done in DGVM simulations as well (Schaphoff et al. 2018a/b, von Bloh et al. 2018). The management data will be held constant on the first known level.

6. LULUC data – are these data all provided as area within each grid cell (or percent of a grid)? I think so, but please indicate. A supplemental table with the cross-walk between the LUH2 and the 17 crop groups used in this study should be included.

Answer to 6.:
Yes, all area data are in hectares and meant to represent the area within each grid cell. We will indicate that more clearly. Additionally, we will add a table to the supplemental material.

7. Please include units for eq 9 – I don’t follow the AGR calculation – it sounds like you are adding biomass and area together. Additionally, HI is usually defined as CP divided by total above ground biomass, so CP x HI is a meaningless number.L

Answer to 7.:
Our harvest index for the yield (t/ha) is calculated based on a linear function with positive intercept (ha) and a slope dependent on the yield (t/ha). This allometric function accounts for the fact that higher-yielding crops often have a lower harvest index than low-yielding crops. In our revised manuscript, we will rewrite the equations to make the functional form more visible. Instead of 
AGR_i,t,cg = CP_i,t,cg ·HI_prod,cg +CA_i,t,cg ·HI_area
we now write
AGR_i,t,cg = CA_i,t,cg (Y_i,t,cg ·HI_prod,cg + HI_area)
We will also add more explanations to the text.

7. Lack of validation. There appears to be no attempt to validate the model or the input data used to drive the model. In general, there is a lack of quantitative evaluation throughout.  There are just two qualitative quality assessments – a table comparing calculated stock change factors to Tier I estimates and a discussion on how the map looks similar to other SOC maps.

Answer to 7.:
To address the raised issue, we will add to our analysis:
* A grid level comparison of SOC stock results to SoilGrids 2.0 and LPJmL to improve spatial evaluation of our results.
* More literature comparison of our derived agricultural land emissions as they are next to the SOC stocks the most central outcome of our analysis.
* An extended qualitative discussion of uncertainty and where it might be the largest.

8. The  model  itself  was  developed  recently  as  part  of  the  2019  Refinements  to  IPCC Guidelines and those updated guidelines discuss how the model was calibrated to a set of long-term trial sites but do not report any model performance metrics. As pointed out by the authors some areas of central EU and the UK more than double SOC undercurrent agriculture than under native vegetation.  This is certainly indicative that there should be some checks against real data (see detailed elaboration on this point further down in this review).  It could be argued that point-based validation for a model run at0.5 degree resolution is meaningless but it would be an interesting exercise to see how the model reproduces trends with known SOC histories.

Answer to 8.:
Our updated model does not show the superising behaviour of strongly increasing SOC stocks in UK and central EU anymore due to the bugfix within the model and the corrected fodder production data. We will add a more detailed spatial comparison to SoilGrids 2.0 (SOC stock estimates based on point data measurements) and other model based SOC estimates (LPJmL) to account for the missing spatial dimension of model output evaluation,

9. Issues with residue C return. Given that the major takeaway from this paper is that the SOC is being sequestered due to improved yield leading to increased residue return, is there any empirical evidence that C inputs to the mineral soil have nearly doubled (Fig 3)? I think the method for calculating residue return to the soil is potentially flawed leading to this large apparent increase. The authors have assumed that both harvest index (HI) and root-to-shoot(RS) ratios have been constant through time.  However, yield improvements over the last century, and in particular the last 50 years, are a result of improvements in genetics and nutrition.  Breeding has resulted in the ability to plant most crops at much higher densities and selection towards more photosynthate being allocated to harvestable organs.  Both of these improvements have altered HI and RS ratios.  Additionally, there are strong interactions between N fertilization rate and root density.  There is a huge literature on crop breeding that support the nonstationarity of these important parameters.

Answer to 9.:
This is a very valid point that we tried to take up in the discussion part as well. We add more detail to the discussion and would like to point out the following thing:
The IPCC methodology, which we use here, tries to capture the effect of a shifting harvest index by making the harvest index a linear function of yield with a positive intercept. The parametrization of this dynamic harvest index was not possible for all crops due to a lack of literature estimates, but the most important crops like cereals or soybeans are captured.

10. Units – Gt and Mt are not SI units, please use Pg and Tg

Answer to 10.:
As In the integrated assessment community tons is most often used for reporting emissions, tons seemed the natural choice for reporting anthropogenic emissions. 
We now came aware that in natural science the Si unit system is the standard unit system. We will change all units to SI and add non-SI units in brackets were needed to bridge to IAM modelling community.

11. L13 (and elsewhere) – “we also find that SOC is very sensitive...” – this is in reference to an unvalidated model result. I’d suggest rewording these sorts of phrases to, “Our model results suggest that SOC is very sensitive...

Answer to 11.:
We will do a careful revision of naming and framing of the evaluation related statements.

12. L279 – “we provide the first world map” – no, you did not. All of the global maps that have been developed using a statistical environmental-covariate modeling approach(i.e. soilgrids and similar) implicitly include all historic land management.

Answer to 12.:
This is correct. We will rewrite the paragraph.

13. It is great that all the data are provided but I found the Karstens 2020a repository to be confusing. Can you have a description for each file in the repository? The naming convention is not clear. I did not want to download 9 Gb of data to figure it out.

Answer to 13.:
We will follow this suggestion and will add more detail to the README file including a description for each file.

14. Fig 1 – perhaps it is just the spatial scale of these small maps (and I haven’t downloaded the results to explore in more detail) but it looks like there is zero intact forest in the Congo Basin and very little intact forest in the Amazon. Also, I would have likedto see a map showing the trend in SOC spatially – how are the 4 Pg C that has been sequestered been spread across the globe? Is it all in Central EU and UK?

Answer to 14.:
Fig 1.(a) is showing cropland SOC,for every grid cell containing cropland without giving an information on the extend of cropland. We will mask out cells with very low cropland area shares, as they might let to the impression of greater cropland extent within large parts of intact forest area. We will also provide a total SOC map in the appendix.

15. Fig 2 – this is a really interesting way of summarizing the model results
Answer to 15.:
Thanks.

16. Fig 4 – the finding presented here is very counterintuitive to me. Why is the SOC debt halved when the model is initialized with natural vegetation? Shouldn’t the 1975 SOCdebt be much greater if the 1901 starting point was natural vegetation instead of actual land use? Perhaps I am just misunderstanding this sensitivity analysis.

Answer to 16.:
The initialization analysis was meant to help the reader understanding the potential maximal error of underestimating on-going emissions on croplands, that where converted to croplands before 1901. We extended the spin-up phase till 1510 now. We will move the initialization analysis to the appendix and improve the caption of the figure to make its interpretation clearer there..

17. Discussion section – in general, there is very little discussion of how these results fit into the large literature on SOC. There are many places were a reference or two would great increase the credibility of the statements that are being made.

Answer to 17.:
We will include more connections to existing literature here.
Section 4.2 – I think this section should come right before the conclusions especially as you refer to analysis that is only presented for the first time in section 4.3
Section 4.3 will be moved to the end of the result as evaulation results subsection.

18. L358-360 – the finding that northern temperate zones (particularly in EU and UK) now have SOC levels up to twice that of native state yet tropical soils have lost 40-70% of their SOC is problematic and, as the authors point out in relation to the EU example,likely points to issues with getting C input to soil correct. The EU has the perfect data set to test this model finding – the EU JRC LUCAS survey was a balanced sampling design between forested and agricultural land uses. In the tropics, it has been fairly well documented that already infertile tropical soils do not lose nearly as much SOC as their fertile temperate zone soil counterparts. While there are issues and large scale generalizations in the IPCC Tier I default factors, they do represent the consensus literature on the topic. The updated meta-analysis between the 2006 and 2019 IPCCC5guidelines when this emission factor for the tropics changed dramatically (see Table 4in this MS) points to this new knowledge.

Answer to 18.:
After our bugfix SOC stocks for the EU do not gain SOC compared to natural vegetation anymore. In general all carbon stocks are much smaller and show much higher losses compared to the Tier 1 approach for both temperate and tropical soils. This might very well still point to missing accounting of carbon inputs to the soil and will be discussed in more detail in the discussion part.
The comparison to point data is however challenging, also as point measurements do not well capture the landscape average and will likely show a very high variance. On the one hand the LUCAS database is given as soil carbon density and would need consistent bulk density data to be comparable to our results. A full comparison to point measurements may also exceed the scope of this first article. We hope with our additional comparison to SoilGrids 2.0 might help fill the evaluation gap here as SoilGrids 2.0 is based on point measurements.

19. L396 – how is this validation? It is just a comparison.

Answer to 19.:
Naming and framing of the evaluation of our results will be improved.

20. L400-406 – there is a large literature that can be drawn upon to support some of the claims made in this section.

Answer to 20.:
We will add more detail and references here

21. Section 4.4 – I do not think this is a valid comparison because SoilGrids explicitly tried to capture high carbon density soils well while your model explicitly excludes organic soils. I suggest applying an agriculture mask to all of these data sets and then redo the analysis. Additionally, ISRIC released an update to SoilGrids >6 months ago that focuses primarily on mineral soil carbon stocks. This update is probably a better comparison.

Answer to 21.:
We included the recommended SoilGrids 2.0 data for a more spatially detailed evaluation of our results especially for cropland soils.

22. L425-428 – this seems out of place.

Answer to 22.:
We will include sensitivity discussions in our extended discussion on evaluation and uncertainty of our results.

23. L453 – comparison to 4p1000 is not really fair because your model is really just the business-as-usual scenario with SOC gains simply because yields are improving glob-ally. 4p1000 is about intentional management shifts to increase SOC.

Answer to 23.:
We agree with the reviewer, that the comparison is a bit misleading. We still think, it is fruitful to compare the observed rates with ambitious targets and will reframe the discussion on this point.

### 2021-06-07 Revisions/Point by point replies - second reviewer.md

# Point by point replies - second reviewer

0. The authors have conducted a study evaluating the influence of management on soil organic carbon in global croplands. This is an important topic for consideration of greenhouse gas mitigation with natural solutions for climate change policy and pro-grams such as the 4 per mille initiative. As the authors mention, there are few studies that have evaluated cropland management effects on soil organic carbon, and possibly none that have addressed the influence at a global scale. The result that increased residue return to soils is the leading driver of carbon changes over the past few decades in croplands is an important finding. As the authors note, the 4 Gt C increase in carbon is less than the goals of the 4 per mille initiative, which some have argued is not realistic. I have a few concerns about the study after review of the IPCC documentation on the method that the authors selected for this analysis. I would suggest that the authors make revisions before the manuscript is accepted.

Answer to 0.:
Dear reviewer, thank you for the thorough and helpful review of our manuscript. While checking and revising our processing in response to your and the other reviewer's feedback, we discovered a bug in the very core of the soil model, leading to an overestimation of the transfer of carbon from active to the slow pool *just* for cropland. Additionally, we found unreasonable high forage crop production values (specifically for pumpkins used as fodder) in our input data, which were taken from FAO statistics. 
This made the overall intensification trend in agriculture lead to increasing carbon stocks in cropland. After correcting the bugs, this is no longer the case. 
Whereas this implies major revisions of our discussion and interpretation of results, we find that the essence of the paper, which is a) the availability of a soil carbon model that can account for changes in agricultural management and can be applied within integrated assessment frameworks and b) an analysis of the importance of accounting for management dynamics in SOC assessments, remains unchanged, albeit modified. We provide an assessment of how results changed after correcting the bugs as a supplement to this authors comment. Here, we respond point-by-point to the reviewers' comments. Where appropriate, this will also address the implications of the bugfix. We look forward to your response.

1. The Tier 2 method is in a croplands chapter of the IPCC report. The documentation in the report states that the model would need to be parameterized for other land uses.Did the authors parameterize the model for other land uses that would be considered natural vegetation? If not, the estimation of soil organic carbon for natural vegetation may not be valid. The authors seem to suggest that this is a possibility in Section 4.4 when stating the soil organic carbon and debt from land use change have to be interpreted with caution. If the model has not been parameterized for natural vegetation, I would suggest that the authors focus on cropland model results, and remove the carbon debt results. The results for the cropland alone are important, and deserve publication even if the natural vegetation estimates are not valid with this model.

Answer to 1.:
This is an important point. While our analysis focuses on croplands, estimating the natural soil carbon stocks is a necessity to account for the C entering the cropland budget via land conversion. Apart from this process, we only use natural vegetation SOC to make our results comparable to other global estimates for validation purposes.
To improve the parametrization of natural soil carbon, we will include the following model updates:
* We will improve the litterfall parameterization in natural vegetation.
* We will compare our results on soil stock under natural vegetation with the results of a model parametrized for natural vegetation (LPJmL).

2. Is it possible to estimate uncertainty with this method? IPCC methods often have large uncertainty but does this method have less uncertainty because it is a Tier 2method. If it is not possible to estimate uncertainty could the authors speculate on the level of uncertainty in the predictions. Knowing something about uncertainty would be helpful in comparisons to the modeled results from other studies that are shown in the manuscript.

Answer to 2.:
The quantitative assessment of the uncertainty of our projections unfortunately exceeds the scope of this article and would likely require a study on itself. The model includes a high number of parameters, and for most of these the uncertainty distributions have not been quantified so far. Moreover, we think that beyond parameter uncertainty, the structural uncertainty from the model design is also very high.

To still address the uncertainty within this manuscript, we will therefore discuss the uncertainty qualitatively. Most of the uncertainty in our view is included in the management data, especially in the manure numbers, as they are calculated from feed data. Additionally residue and litter estimations are based on the set of global parameters, that contains large uncertainty and at the same time have a great impact on the overall size of carbon inputs to the soil. Both effects will be discussed in more detail.

3. The authors state that a sensitivity analysis presented in Figure 4 shows that management impact is robust to the initialization of the soil organic carbon stocks at the beginning of the spin-up phase. But, the stocks and change in stocks almost halves the values if the initialization is done with natural vegetation. The initialization does make a difference, and needs further explanation.

Answer to 3.:
It is correct that the SOC stocks are highly dependent on the legacy of management. Figure 4 made however clear, that the SOC gap - so the difference between a baseline scenario and a counterfactual scenario with constant management - was not strongly dependent on the initialization. We thereby showed that the initialization does not affect our central finding.

Still, in order to improve our estimates also for the absolute SOC stock, we now extended the length of the spin-up phase, starting in 1510 (default spin-up start for introducing land use in simulations with LPJmL, see e.g. Schaphoff et al. 2018a/b, von Bloh et al. 2018 ). We will analysis and discuss our results with respect to the initialization in more detail.

4. Good to see that the authors have made a comparison to another approach to confirm the Tier 2 results. The Tier 1 method provided by the IPCC has been used for this purpose. In section 2.2, the authors present a method estimating stock change factors instead of soil organic carbon changes. But, the results in Table 4 for the stock change factors are not convincing that the methods are consistent, and the text seems unclear with discussion about larger differences with the IPCC 2019 values, which were updated by the authors and should be more accurate – I would think. Why not estimate the change in soil organic carbon for a direct comparison with the Tier 2 method instead of the stock change factors? Also, the placement of these results after the discussion seems odd, and conventionally would be presented in the results section before discussion.

Answer to 4.:
Thank you for the recommendation. We will place the comparison within the result section. For a Tier 1 approach the change in soil organic carbon has to be calculated based on a reference stock. The default stocks given by the IPCC have very low spatial resolution (42 coarse climate zone and soil type specific values), which leads to additional uncertainty when comparing directly changes in soil organic carbon.
We will add more detail to the discussion about the strong deviation of 2006 and 2019 default stock changes factors.

5. Figure 3 shows results from making certain practices constant from 1975 to 2010.The authors state around line 315 that the effect of no-till has been strong since 1990,but the effect seems minor and may not differ statistically from the histManagement with uncertainty. The conclusion about the importance of residue seems most important here.

Answer to 5.:
Due to the overall changes to the results, we will rewrite major part of the result and discussion. We will take more thoroughly into account effects of uncertainty.

6. The authors suggest that there needs to be a circular flow with food supply chain back to soils. They assumed that none of the waste from supply chains are returned to soils (near line 300) but this seems incorrect. Municipal waste and materials are amended to soils in many regions of the world although maybe there are no data on these amendments? If this is the issue, the authors could mention that they are making a conservative assumption due to lack of data.

Answer to 6.:
Indeed, further soil inputs include the application of human excreta and sewage sludge, as well as the application of processing wastes, forestry residues or biochar. Unfortunately, data on the quantity of these inputs is very scarce and often does not exist with global coverage.
In the draft of the International Nitrogen Assessment (will be provided confidentially to the reviewer), the available literature estimates for these flows (in regard to nitrogen) were reviewed. So far no reliable estimates exist, but the existing estimates indicate that these inputs must be by an order of magnitude lower than those by crop residues and manure.

7. The authors evaluate the sensitivity of the Tier 2 model for tree litter with methods in Section 2.4.3. The Tier 2 model divides litter into metabolic and structural components,and the authors have averaged lignin to nitrogen across tree components as input to the model. But forest also include deadwood and should be separated from other forest litter to model decomposition. Did the authors add a deadwood pool? I question if this model is appropriate for forest if deadwood is not modeled separately.

Answer to 7.:
We follow this suggestion and will add more detail on the litterfall of the natural vegetation. Using additional information from LPJmL, we will split up the litterfall into a wood- and soft-tissue fraction and add different parameterizations for these. 
We will not be able to add a deadwood pool, since that would require additional parameterization of turnover dynamics for this new pool. Deadwood pools are also not treated explicitly in many DGVMs but are considered part of litter pools, which distinguish woody from non-wood litter pools. The separation of litterfall into wood and soft tissue fluxes will thus add similar stock detail as in DGVMs.

8. Recommend that the authors provide more explanation for Equation 9, which determines the residue amount of C, and is a key driver of the carbon change. Harvest index is the proportion of plant biomass that is harvested, but the authors are multiplying the harvested crop product by the harvest index. But the conventional approach is ’harvested crop production divided by the harvest index’ to determine the total biomass and then subtract the harvested amount to estimate the residue. The authors are accounting for double harvesting and fallow in this calculation, which I agree is important, but some further explanation is needed about the calculation to understand how residue carbon is estimate from crop production, harvest index and area.

Answet to 8.:
Our harvest index for the yield (t/ha) is calculated based on a linear function with positive intercept (ha) and a slope dependent on the yield (t/ha). This allometric function accounts for the fact that higher-yielding crops often have a lower harvest index than low-yielding crops. In our revised manuscript, we will rewrite the equations to make the functional form more visible. Instead of 
AGR_i,t,cg = CP_i,t,cg ·HI_prod,cg +CA_i,t,cg ·HI_area
we now write
AGR_i,t,cg = CA_i,t,cg (Y_i,t,cg ·HI_prod,cg + HI_area)
We will also add more explanations to the text.

9. For the Tier 1 method, IPCC divides the reference carbon stocks by climate and soil types. Did the authors also divide the grid cells by climate and soil because only climate is mentioned in the text? And, I found a diagram in Figure 5.1 in the IPCC report that divides low, medium and high input categories. Did the authors use this diagram to classify the input? It is not clear if the authors use the diagram or developed their own. If they developed their own, is it consistent with the IPCC factors?

Answer to 9.:
We do not calculate carbon stocks and stock changes based on the Tier 1 method. Instead we calculate stock change factors from our Tier 2 approach to compare only these factors to the Tier 1 factors as given within the guidelines. We will point this out more clearly in the method and discussion part. In addition, we note here:
* To our knowledge, the IPCC method splits up soil types into mineral and organic. This analysis focuses exclusively on mineral soils, which will be pointed out clearler  throughout the paper. 
* To aggregate our Tier 2 results we assigned only one climate type for each grid cell (the most dominant one). 
* The Tier 2 method does not take into account different soil classes directly, but rather takes the sand fraction as a proxy for soil properties (like water holding capacities). .
* For the Tier 1 method no detailed analysis has been conducted . All factors shown in the manuscript are default factors without any spatial disaggregation of effects. We did not classify the inputs into Tier 1 categories (as there was no need to do so for Tier 2 and no data available to do so at the global scale).

10. What is ‘resp’ is ‘area reduction resp’ on line 110? This sentence should be revised to improve readability. I also found other sentences that were difficult to read or missing words in some cases, but did not make a list during my review. Suggest a careful review before final publication.

Answer to 10.:
We will do so.

11. I found the Tier 2 method in Chapter 5 of Volume 4 of the 2019 IPCC report, and would suggest that the authors cite this chapter rather than the entire 2019 IPCC report,which has 5 volumes. This would make it easier for others interested in the study to find the method in the IPCC report.

Answer to 11.:
We will change the citation from full report to the Chapter 5 were needed.

### 2021-07-24 ResultNotebooks/investigate_SOCbugfixDiff.Rmd
update results scripts

* We discovered a bug in the very core of the soil model, leading to an overestimation of the transfer of carbon from active to the slow pool *just* for cropland. In regions with high carbon inputs (e.g. UK or Central EU) this let to unreasonable high SOC stocks.
* Additionally, we found unreasonable high forage crop production values (especially for pumpkins used as fodder) in our input data, we used from FAO. This let to an additional decrease of residue inputs to the soil for several countries (including, Australia, Belgium and Germany). 
* We moreover improved the spin-up of our model by accounting for land-use change since 1510.

The SOC debt is not decreasing anymore, but still continuing to increase, which is visible in the following figure.

```{r captionSOCdebt, echo=FALSE}
captionSOCdebt <- "NEW!!! $\\Delta SOC$ is the difference between SOC under historic land use and potential natural vegetation and is also called the SOC debt. Within the period 1975 -- 2010 the SOC debt is continuing to increase."
```

```{r image_grobs, fig.show='hold', out.width = "70%", fig.align = "default", echo=FALSE, fig.cap = captionSOCdebt,}
library(cowplot)
library(ggplot2)

ggdraw() + draw_image("../ResultNotebooks/Output/Images/SOCemis.png")

```

@@

```{r captionSOCmaps, echo=FALSE}
captionSOCmaps <- "NEW!!! (a): Distribution of total global SOC stocks for the first 30 cm on cropland: Carbon stocks are large in high yielding areas. (b)+(c): Absolute (b) and relative (c) SOC stocks changes compared to a potential natural state identify different hotspots of SOC dynamics. Whereas absolute losses $\\Delta SOC$ are often highest in temperate dry regions, relative losses $F^\\mathrm{SCF}$ are often larger in tropical moist areas. (d): $\\Delta SOC$ between SOC under historic land use and potential natural vegetation is stopping to decrease vs. actally decrease over the the period 1975--2010. "
```

```{r SOCmaps, out.width = "16cm", fig.cap = captionSOCmaps, echo=FALSE, fig.pos="h"}
# All defaults
knitr::include_graphics("../ResultNotebooks/Output/Images/4panelfigure.png")
```
```{r SOCmaps2, out.width = "16cm", fig.cap = "OLD!!!", echo=FALSE, fig.pos="h"}
# All defaults
knitr::include_graphics("../../oldPaperVersion/ResultNotebooks/Output/Images/4panelfigure.png")
```
\pagebreak

With the figures above we provide a world map of SOC stocks for the first 30 cm on croplands considering historic management data at the global scale for the year 2010. Values ranging between well over $100\mathrm{t ha^{-1}}$ in northern temperate croplands to less than $5\mathrm{t ha^{-1}}$ for arid and semiarid croplands.

@@

```{r captionSOCscen, echo=FALSE}
captionSOCscen <- "NEW!!! (a) Global $\\Delta SOC$ in GtC for different management scenarios: The stylized scenarios devate from historic argicultural management by holding effects of carbon inflows from residues, manure constant or neglecting adoption of no-tillage practices. ConstManagement combines all three modifications. Note that $\\Delta SOC$ is defined as the difference of SOC under land-use compared to a natural vegetation state. Figure (b) shows the carbon inflows from crop residue and manure."
```

```{r SOCscen, out.width="10cm", fig.cap = captionSOCscen, echo=FALSE}
# All defaults
knitr::include_graphics("../ResultNotebooks/Output/Images/scenario_horiz.png")
```
```{r SOCscen2, out.width="10cm", fig.cap = "OLD!!!", echo=FALSE}
# All defaults
knitr::include_graphics("../../oldPaperVersion/ResultNotebooks/Output/Images/scenario_horiz.png")
```

@@

Stock change factors $F^{\\mathrm{SCF}}$ in comparison to IPCC Tier 1 default factors: Our updated results are much smaller and still too low compared with the default values of the IPCC in general.

```{r SCFglo, echo=FALSE,  results = 'asis'}
table <- readRDS("../ResultNotebooks/Output/SFC_comparison.rds")
library(xtable)
print(xtable(table$comparison_table, digit=2, label="tab:SCFglo",
             caption="NEW!!!"),
               comment=FALSE)
```

```{r SCFglo2, echo=FALSE, results = 'asis'}
table <- readRDS("../../oldPaperVersion/ResultNotebooks/Output/SFC_comparison.rds")
library(xtable)
print(xtable(table$comparison_table, digit=2, label="tab:SCFglo",
              caption="OLD!!!"), comment=FALSE, caption.placement = "top")
```

>>>>

* We discovered a bug in the very core of the soil model, leading to an overestimation of the transfer of carbon from active to the slow pool *just* for cropland. In regions with high carbon inputs (e.g. UK or Central EU) this let to unreasonable high SOC stocks.
* Additionally, we found unreasonable high forage crop production values for pumpkins used as fodder in our input data, we used from FAO. This led to an additional decrease of residue inputs to the soil for several countries (including, Australia, Belgium and Germany). The values were excluded and replaced by zeros. 
* We moreover improved the spin-up of our model by accounting for land-use change since 1510.

## Summary of main changes

The SOC debt is not decreasing anymore, but still continuously increases. Unreasonable high numbers for SOC stocks and stock change factors compared to natural vegetation stocks have vanished. The impact of management is lower but still considerably. Stock change factors for cropland SOC are now globally lower than default factor from the IPCC for all four climate zones.

In the following, we provide the comparison of updated (first) and original (second) figures for three of our main results:

* SOC distribution and depletion (Fig. 1 in the manuscript)
* Agricultural management effects on SOC debt (Fig. 3 in the manuscript)
* Modeled management effect in comparison with default IPCC Tier 1 factors (Tab. 4 in the manuscript)

@@

```{r captionSOCmaps, echo=FALSE}
captionSOCmaps <- "Updated figure! (a): Distribution of total global SOC stocks for the first 30 cm on cropland: Carbon stocks are large in high yielding areas. (b)+(c): Absolute (b) and relative (c) SOC stocks changes compared to a potential natural state identify different hot spots of SOC dynamics. Whereas absolute losses $\\Delta SOC$ are often highest in temperate dry regions, relative losses $F^\\mathrm{SCF}$ are often larger in tropical moist areas. (d): SOC debt is the difference between SOC under historic land use and potential natural vegetation. Within the period 1975 -- 2010 the SOC debt is continuing to increase."
```

```{r SOCmaps, out.width = "16cm", fig.cap = captionSOCmaps, echo=FALSE, fig.pos="h"}
# All defaults
knitr::include_graphics("../ResultNotebooks/Output/Images/4panelfigure.png")
```
```{r SOCmaps2, out.width = "16cm", fig.cap = "Original figure of the manuscript", echo=FALSE, fig.pos="h"}
# All defaults
knitr::include_graphics("../../oldPaperVersion/ResultNotebooks/Output/Images/4panelfigure.png")
```
\pagebreak

With the figures above we provide a world map of SOC stocks for the first 30 cm on croplands considering historic management data at the global scale for the year 2010. Values ranging between well over $100\mathrm{t ha^{-1}}$ in northern temperate croplands to less than $5\mathrm{t ha^{-1}}$ for arid and semiarid croplands.
The correction of to high SOC stock values is visible for all four figure parts, as it corrects the unreasonable high values in UK and Central Europe (see old figure).

@@

```{r captionSOCscen, echo=FALSE}
captionSOCscen <- "Updated figure! (a) Global $\\Delta SOC$ in GtC for different management scenarios: The stylized scenarios deviate from historic agricultural management by holding effects of carbon inflows from residues or manure constant, or neglecting adoption of no-tillage practices. ConstManagement combines all three modifications. Note that $\\Delta SOC$ is defined as the difference of SOC under land-use compared to a natural vegetation state. Figure (b) shows the carbon inflows from crop residue and manure."
```

```{r SOCscen, out.width="10cm", fig.cap = captionSOCscen, echo=FALSE}
# All defaults
knitr::include_graphics("../ResultNotebooks/Output/Images/scenario_horiz.png")
```
```{r SOCscen2, out.width="10cm", fig.cap = "Original figure of the manuscript", echo=FALSE}
# All defaults
knitr::include_graphics("../../oldPaperVersion/ResultNotebooks/Output/Images/scenario_horiz.png")
```

@@

Stock change factors $F^{\\mathrm{SCF}}$ in comparison to IPCC Tier 1 default factors: Our updated results are much smaller and still considerably lower compared to the default values of the IPCC for all four climate zones.

```{r SCFglo, echo=FALSE,  results = 'asis'}
table <- readRDS("../ResultNotebooks/Output/SFC_comparison.rds")
library(xtable)
print(xtable(table$comparison_table, digit=2, label="tab:SCFglo",
             caption="Updated table."),
               comment=FALSE)
```

```{r SCFglo2, echo=FALSE, results = 'asis'}
table <- readRDS("../../oldPaperVersion/ResultNotebooks/Output/SFC_comparison.rds")
library(xtable)
print(xtable(table$comparison_table, digit=2, label="tab:SCFglo",
              caption="Original table of the manuscript."), comment=FALSE)
```
